A thesis draft

### 2018-10-10 draft.tex
Fix grammar error
Add openbaton paragraph

TUN/TAP and IP Encapsulation within IP (initially defined in RFC 2003 with the 
aim to deliver IP packets over Mobile IP for mobile networks) maintain the 
connection transparency incapsulating the packet in another one.
\begin{figure}[t]
  \centering
  \includegraphics[scale=0.5]{IPoverIP}
  \caption[IP Encapsulation within IP packet schema]{An schema of IP 
Encapsulation within IP. Is noticeable how the original packet becomes the 
payload of a new one, thus being encapsulated. All the informations regarding 
the original packet remains untouched: when this kind of packet gets send 
from a machine to another, the OS will remove the new packet header and will 
present to the user-space program receiving the data its payload: a IP 
packet. Packets encapsulation can be applied with higher layers too, thus 
allowing for TCP and UDP packet incapsulation.}
  \label{chap:prjan:img:ip_over_ip}
\end{figure}

@@

\subsubsection{Other technologies}\todo{Talk somehow of the other tecnhologies}
\paragraph{Openvswitch}
\paragraph{Openbaton} Created by the Institute Fraunhofer, it's a open-source, 
customizable NFV MANO-compliant framework, that offers many configurations 
options, and since it's written in Java, there is the possibility to add 
components (plug-ins) dynamically. Openbaton can be installed on-permise 
installations but it can also run on Docker containers. It's designed to work 
with cloud providers like Amazon or Google Compute engine, but it offers 
compability with on-permise cloud solutions like Openstack too.
\begin{figure}[h]
 \centering
 \includegraphics[scale=0.45]{openbaton_logo}
 \caption{Openbaton logo}
 \label{chap:prjan:img:openbaton_logo}
\end{figure}

>>>>

TUN/TAP and IP Encapsulation within IP (initially defined in RFC 2003 with the 
aim to deliver IP packets over Mobile IP for mobile networks) maintain the 
connection transparency incapsulating the packet in another one.
\begin{figure}[t]
  \centering
  \includegraphics[scale=0.5]{IPoverIP}
  \caption[IP Encapsulation within IP packet schema]{A schema of IP 
Encapsulation within IP. Is noticeable how the original packet becomes the 
payload of a new one, thus being encapsulated. All the informations regarding 
the original packet remains untouched: when this kind of packet gets send 
from a machine to another, the OS will remove the new packet header and will 
present to the user-space program receiving the data its payload: a IP 
packet. Packets encapsulation can be applied with higher layers too, thus 
allowing for TCP and UDP packet incapsulation.}
  \label{chap:prjan:img:ip_over_ip}
\end{figure}

@@

\subsubsection{Other technologies}\todo{Talk somehow of the other tecnhologies}
\paragraph{Openvswitch}
\paragraph{Openbaton} Created by the Institute Fraunhofer, it's a open-source, 
customizable NFV MANO-compliant framework, that offers many configurations 
options, and since it's written in Java, there is the possibility to add 
components (plug-ins) dynamically. Openbaton can be installed as a normal 
computer program (they offer packages for the most common distros) but it can 
be deployed on Docker containers too. It's designed to work with cloud 
providers like Amazon or Google Compute engine, but it offers compability with 
on-permise cloud solutions like Openstack, where it deploys virtual machines 
using the API the platform offers. It can store VNF configurations saved as 
TOSCA YAML\todo{What does TOSCA mean? Find out} and it can handle multiple 
PoPs\todo{Write down PoP meaning}. It offers a VNF lifecyle management 
out-of-the-box, with the possibility to customize it based on the user needs. 
Its modular design allows developers to change parts of the codebase with 
custom ones, making the product really flexible to different platforms. 
Performing this operation requires a deep knowlege of the framework though.
\begin{figure}[h]
 \centering
 \includegraphics[scale=0.45]{openbaton_logo}
 \caption{Openbaton logo}
 \label{chap:prjan:img:openbaton_logo}
\end{figure}
